Effect of character correlation

### 2018-03-28 Analysis/04-EffectCorrelation_lm.Rmd
added beta regressions (?)

## Running the model
model_out <- run.lm(matrices_cd, whole_data, chain = "25t_100c", method = "Bayesian", metric = "RF", cent.tend = NULL)

@@

```{r, fig.width=12, fig.height=12, warnings = FALSE}
## Pool all the results into one list
pooled_results <- pool.matrix.cd(all_matrices_cd, length.out = 28)

# ## Running the model
model_out_bay_RF <- run.lm(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "RF", cent.tend = NULL)
model_out_bay_Tr <- run.lm(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "Triplets", cent.tend = NULL)
model_out_par_RF <- run.lm(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "RF", cent.tend = NULL)
model_out_par_Tr <- run.lm(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "Triplets", cent.tend = NULL)

## Plotting the output
par(bty = "n", mfrow = c(2,2))
one.correlation.plot(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "RF", model_out_bay_RF, cent.tend = NULL, legend = TRUE, main = "Bayesian", xlab = "RF")
one.correlation.plot(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "RF", model_out_bay_Tr, cent.tend = NULL, legend = FALSE, main = "Bayesian", xlab = "RF")
one.correlation.plot(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "Triplets", model_out_par_RF, cent.tend = NULL, legend = FALSE, main = "Parsimony", xlab = "Triplets")
one.correlation.plot(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "Triplets", model_out_par_Tr, cent.tend = NULL, legend = FALSE, main = "Parsimony", xlab = "Triplets")
```

@@

@@

@@

>>>>

## Running the model
model_out <- run.lm(matrices_cd, whole_data, chain = "25t_100c", method = "Bayesian", metric = "RF", cent.tend = NULL)
model_beta <- run.lm(matrices_cd, whole_data, chain = "25t_100c", method = "Bayesian", metric = "RF", cent.tend = NULL, type = "beta")

@@

```{r, fig.width=12, fig.height=12, warnings = FALSE}
# ## Pool all the results into one list
# pooled_results <- pool.matrix.cd(all_matrices_cd, length.out = 28)

# # ## Running the model
# model_out_bay_RF <- run.lm(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "RF", cent.tend = NULL)
# model_out_bay_Tr <- run.lm(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "Triplets", cent.tend = NULL)
# model_out_par_RF <- run.lm(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "RF", cent.tend = NULL)
# model_out_par_Tr <- run.lm(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "Triplets", cent.tend = NULL)

# ## Plotting the output
# par(bty = "n", mfrow = c(2,2))
# one.correlation.plot(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "RF", model_out_bay_RF, cent.tend = NULL, legend = TRUE, main = "Bayesian", xlab = "RF")
# one.correlation.plot(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "RF", model_out_bay_Tr, cent.tend = NULL, legend = FALSE, main = "Bayesian", xlab = "RF")
# one.correlation.plot(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "Triplets", model_out_par_RF, cent.tend = NULL, legend = FALSE, main = "Parsimony", xlab = "Triplets")
# one.correlation.plot(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "Triplets", model_out_par_Tr, cent.tend = NULL, legend = FALSE, main = "Parsimony", xlab = "Triplets")
```

@@

<!-- only 75t_100c correctly passes the lm assumptions -->

@@

<!-- only 75t_100c and 150t_100c correctly passes the lm assumptions -->

@@

<!-- only 150t_100c correctly passes the lm assumptions -->
